The landscape of chloroplast genome assembly tools

### 2020-05-21 manuscript/reviewer_response1.tex

\documentclass[a4paper,10pt]{scrartcl}
\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\title{Response to Reviewers}
\author{Markus J. Ankenbrand and Frank F\"{o}rster for the authors}
\date{\today}
%
\begin{document}
\maketitle
% \section{Editor}
% We have now received reports from two referees, whose comments are available below.
% As you will see from the reports, both referees raised serious concerns that the benchmark hasn't provided sufficient advance to be useful for the field.
% At this stage, therefore, we are not persuaded that an offer of publication in Genome Biology would be justified.
% Unless you can address all of the issues raised by the referees I am afraid that we would not be able to consider this work again.
% In particular we ask that you provide additional analyses as requested by both referees to convince them of the advance.
% The revised manuscript should address in full all the points raised by both referees; a separate list of the revisions made, specifying where in the manuscript the changes have been made, would also be helpful.
% Please note that all data generated for the manuscript should be deposited in a relevant public repository, with accession codes listed in the manuscript's Availability of Data and Materials section.
% All other supporting data should also be signposted.
% If you decide to submit a revised version, you will need to  this as a new manuscript, although we would consider it in the same way as we do all revised manuscripts.
% The exception is that we will take into account any work published in the intervening period.
% For the time being, however, we hope that you will find our referees' comments helpful in deciding how to proceed.
% Please feel free to contact us if you have any questions.
\section{Reviewer 1}
Methods are appropriate but same authors developed ChloroExtractor, an important tool used as a benchmark in this study.
Authors compare seven chloroplast genome assembly tools.
So, this reviewer is not sure of novelty of this manuscript.
So, authors haven't addressed the important question "Does the work represent a significant advance over previously published studies?".

\textbf{
Indeed the novelty in this article is not a new approach to the task of chloroplast genome assembly but rather a thorough benchmark of existing tools (including our tool ChloroExtractor).
This represents a substantial advance for the field as there are competing tools published for the same task without any information about their relative performances.
Currently, researchers have to do this evaluation of tools themselves to find the appropriate tool which leads to duplicated efforts as this is done by every group separately and without sharing results.
If this evaluation is neglected a non optimal tool might be used which can lead to additional manual efforts in finishing or additional costs if more data is generated.
Thus, clear guidelines to the end user (and important directions for improvement to the developers) are novel, important and beneficial for the research community.
}

@@

User experience and success rate should be determined by users and documented through satisfaction surveys.
This is especially important when authors emphasize that program can be used using standard computer infrastructure.

\textbf{
We agree that this would be the best way to measure and quantify user experience.
However, the main focus of the work was on quantitative performance measures. 
Nevertheless, we decided to include usability metrics that were obtainable in a defined and structured way using the reviewer guidelines of the ``Journal of Open Source Software'' (JOSS).
}

@@

There is >1,000 sequenced chloroplast genomes, with a large majority not fully assembled or annotated.
So, authors have plenty of opportunity to demonstrate use of these new assembly tools.

\textbf{
Thanks for pointing this out.
We now include as a proof of principle the application of these tools on 105 novel data sets.
The assembly of 49 of those 105 data sets returned chloroplast genomes.
After further screening against NCBI databases, still 20 data sets remained.
That sets contained new chloroplast genomes for species without a reported plastid genome.
We thus clearly demonstrate that the insights from this article can be used to produce further novel results that can lead to further biological insight.
}

@@

It is well known that intergenic spacer regions are not conserved and not even a single intergenic spacer region is conserved within chloroplasts genomes of the graminae or grass genomes.
Intergenic spacer region occupies >50\% of the genome.
So, how does reference genome help in genome assembly?

\textbf{
This is a very interesting question.
But due to we are comparing de novo assembly tools, we think answering this question is outside the scope of our publication.
Nevertheless, using reference plastid genomes, is helpful to sort the huge amount of input data into potential plastid genome related sequences and non related sequences which need no longer to be considered for an assembly.
%TODO: some people use it, some programs use it, it seems to work often but actually your argument is justification why we restricted our analysis to de novo tools.
}

@@

In order to have real life comparison, authors could have sequenced few chloroplast genomes and used that data to compare different assembly tools and time taken for each program, pros and cons.

\textbf{
We already tested the tools on real data sets downloaded from NCBIs SRA which is equivalent to customly sequenced data.
But we now include additional 105 novel data sets with no reference chloroplast in the database.
}

@@

- Is the paper of broad interest to others in the field, or of outstanding interest to a broad audience of biologists?
This is of interest to evolutionary biologists to study phylogenetics or for chloroplast genetic engineering.

\section{Reviewer 2}
This study provides an systematically comparison of the chloroplast assembly tools at first and show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
Moreover, the authors created docker images for each tested tool, which are available for the scientific community and improved reproducibility, thus large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.
This topic of the review paper is knowledgeable and helpful for all the scientists who are working in the field of plant chloroplast assembly.
However, the overall manuscript is not well written and contains limited information about systematically comparison of the chloroplast assembly tools and docker images for assembled reproducibility.

\textbf{
Thanks for your thorough review and the pointers that helped us improve the overall readability of the manuscript.
In addition we received feedback and edits from a native English speaker to further improve readability.
We try to add more information about our systematically comparison into the manuscript, moreover, we provide all our script and even the docker container in our GitHub repository, DockerHub, and Zenodo to enable a maximum of reproducibility.
}

@@

Specific points: The number of lines on the edge does not correspond to the maintext.

The major concerns about this manuscript can be found below and major revision is suggested before publication in "Genome Biology".

\begin{itemize}
    \item Page1  part of "General introduction and motivation"
    \item Line 4: It should be quote recent article
    \item Line 11: It should be quote recent article
    \item Page2
    \item Line 16: It should be IRa and IRb
    \item Line 18: It should be quote recent article
    \item Line 24-27: Re-write sentence
    \item Part of "Approaches to extracting chloroplasts from whole genome data"
    \item Line 6: Delete the dot before the quote
    \item Lines 7-9: Re-write sentence
    \item Part of "Purpose and scope of this study"
    \item Line 2: It should be in italic type
    \item Line 2: It should be genome
    \item Line 3: Raw genomic data sets should be filter out low-quality reads by quality control
    \item Lines 4 and 5: Many command-line tools of de novo assemble for chloroplast genome have all of these features, e.g., MITObim.
    \item Part of "Time requirements"
    \item Line 1: It should be among
    \item Line 4: Different tools with more than 1 gigabyte data sets should be tested, and Figure1 can`t give valuable information as no significant difference for time-consuming. The same question for Part of "Memory and CPU Usage". Why these seven assemblers were chosen to test? Figure should be "Fig." and table as "Table".
    \item Part of "Qualitative"
    \item Line 3: NGS data for crop genomes can`t be used for GetOrganelle? In this part, the same data set should be used to test for every assemblers better.
    \item Part of "Quantitative"  
    \item Part of "Simulated data"
    \item Line 1: Why not show the result for different data sets with every assemblers in Fig.3 and Table 2? Fig.3 and table 2 show no regular pattern in scores except the assembler GetOrganelle obtaining perfect.
    \item Part of "Real data sets"
    \item Line 3: The performance of GetOrganelle was bad, as only 199 circular assemblies out of a total of 356 assemblies that resulted in an output, the percent is 55.9\%, however it achieved a median scores of 99.7. The number "99.7" should to be "89.13", as show in table 3? The SD value of GetOrganelle is too large than the other three tools but it achieved the highest scores.
    \item Part of "Consistency"
    \item Line 3: As shown in the Fig.6, only two tools achieved R2  not equal 1 by re-running assemblies and comparison of the scores of two assemblers, however, GetOrganelle defined as the only tool that succeed in obtaining similar score for all assemblers, this conclusion is not rigorous.
\end{itemize}

\textbf{We addressed the more specific issues within the manuscript.}
\end{document}

### 2020-05-21 manuscript/bmc_article.tex
Update manuscript folder for resubmission

\author[
    addressref={aff1,aff3},
    %noteref={n1},
    email={jan.freudenthal@uni-wuerzburg.de}
    ]{\inits{JAF}\fnm{Jan A} \snm{Freudenthal}}
\author[
    addressref={aff1,aff2},
    email={simon-pfaff@gmx.de}
    ]{\inits{SP}\fnm{Simon} \snm{Pfaff}}
\author[
   addressref={aff1,aff3},
   email={niklas.terhoeven@uni-wuerzburg.de}
]{\inits{NT}\fnm{Niklas} \snm{Terhoeven}}
\author[
   addressref={aff1},
   email={arthur.korte@uni-wuerzburg.de}
]{\inits{AK}\fnm{Arthur} \snm{Korte}}
\author[
   addressref={aff1,aff3,aff4 },
   noteref={n2},
   email={markus.ankenbrand@uni-wuerzburg.de}
]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}
\author[
   addressref={aff1,aff2,aff5},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff1},                       % id of corresponding address, if any
   noteref={n2},                        % id's of article notes, if any
   email={frank.foerster@uni-wuerzburg.de}   % email address
]{\inits{FF}\fnm{Frank} \snm{Förster}}

@@

\address[id=aff3]{%
  \orgname{AnaLife Data Science},
  \street{Wiesengrund 16},
  \postcode{97295 Waldbrunn}
  \city{W\"{u}rzburg},
  \cny{Germany}
}
\address[id=aff2]{%                           % unique id
  \orgname{Department of Bioinformatics, University of W\"{u}rzburg}, % university, etc
  \street{Biozentrum, Am Hubland},                     %
  \postcode{97074},                                % post or zip code
  \city{W\"{u}rzburg},                              % city
  \cny{Germany}                                    % country
}
\address[id=aff4]{%
  \orgname{Chair of Cellular and Molecular Imaging, Comprehensive Heart Failure Center, University Hospital W\"{u}rzburg},
  \street{Josef-Schneider-Str.\ 2},
  \postcode{97080}
  \city{W\"{u}rzburg},
  \cny{Germany}
}

\address[id=aff5]{%
  \orgname{Fraunhofer IME-BR},
  \street{Winchester Str.\ 2},
  \postcode{35394}
  \city{Gie\ss{}en},
  \cny{Germany}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Abstract begins here                 %%
%%                                          %%
%% Please refer to the Instructions for     %%
%% authors on http://www.biomedcentral.com  %%
%% and include the section headings         %%
%% accordingly for your article type.       %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstractbox}
\begin{abstract} % abstract
%One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
Chloroplasts are intracellular organelles that enable plants to conduct photosynthesis. They arose through the symbiotic integration of a prokaryotic cell into an eukaryotic host cell and still contain their own genomes with distinct genomic information.
Plastid genomes accommodate essential genes and are regularly utilized in biotechnology or phylogenetics.
%Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
Different assemblers that are able to asses the plastid genome, have been developed.
These assemblers often use data of whole genome sequencing experiments, which usually contain reads from the complete chloroplast genome as well, as input.

%One sentence clearly stating the general problem being addressed by this particular study.
The performance of different assembly tools has never been systematically compared. %to each other concerning success rate or computational requirements.
%One sentence summarising the main result (with the words “here we show” or their equivalent).
Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of known real data sets.
%Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
The examination of more than \num{100} data sets with unknown plastid genomes led to the assembly of novel chloroplast genomes in almost \SI{50}{\percent} of the cases.
%\todo{on the novel set we only have 49/105 which is roughly 47 percent}
%One or two sentences to put the results into a more general context. 
We created docker images for each tested tool that are freely available for the scientific community and ensure reproducibility of the analyses.
These containers allow to analyze and screen data sets for chloroplast genomes using standard computational infrastructure.
%Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion. 
Thus, large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.

@@

%\todo{Markus/Frank: YES should we host a specific page on the alitv page for all the novels? Here: \url{https://alitvteam.github.io/AliTV/chloroplast_benchmark/})}%
For two assemblies, that were obtained by different assemblers, but not by \go{}, we kept one assembly obtained by \np{} and one from \fp{}. \todo{@frank: please check, my dataset contains 45 GO, 3 FP, 1NP}
The resulting \num{49} sequences have been annotated with GeSeq \cite{geseq} and uploaded to NCBI Genbank (\cref{tab:accessions_suppl}).
The median number of distinct genes annotated were 80 for coding sequences, 4 for rRNA and 27 for tRNA (\cref{tab:feature_count_novel}, \cref{fig:feature_count_novel}). 
%\todo{FRANK: more info about the taxonomic distribution of our novels and how we extended the coverage of the tol}.  %% STILL 2 DO

@@

%\todo{FRANK: Add discussion of novel}  %% STILL 2 DO
% Yes, what have we leraned form the novel chloroplasts .. e.g. gene content 
We observed no phylogenetic pattern in the success rate of the assemblers (\cref{fig:tree}).
This indicates that the tools are generally able to reconstruct chloroplast genomes across the plant kingdom even without available reference genomes.

@@

\section*{Methods}
\subsection*{Data availability}
Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
All docker images are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages}).

@@

\subsubsection*{Real data}
We selected real data deposited at SRA \cite{sra2010}.
We searched all data that matched \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]} \cite{sra_search_term}. 
For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set.
In total, this amounted to \num{369} data sets (\cref{tab:real_dataset_details}) representing a broad spectrum of the green plants (\cref{fig:tree}).
%\todo{Frank: Nochmal was zum Baum schreiben und novels dort mit aufnehmen!}  %% STILL 2 DO

@@

\subsection*{Evaluation Criteria}
\subsubsection*{Computational Resources}
%Due to computational resources are limited, we evaluated the effect of different input parameters.
We recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder for each program. 
As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs sampled from  our simulated reads.
%Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
We used our docker image setup (\cref{tab:dockerimages}) to run all assembly programs three times for each parameter setting.
The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).

@@

\begin{table}[h!]
\caption{\textbf{Docker images used in our benchmark setup} SHA256 checksums are stated in \cref{tab:dockerimages_suppl}}
%\todo{Frank: add software version column (maybe use git describe)} %% STILL 2 DO
\label{tab:dockerimages}
\centering
      \resizebox{\textwidth}{!}{\begin{tabular}{ccc}
        \hline
          Tool & Image name and tag\\ \hline
          \ce & \dockerce \\
          \cassp & \dockercassp \\
          \fp & \dockerfp \\
          \go & \dockergo \\
          \ioga & \dockerioga \\
          \np & \dockernp \\
          \oa & \dockeroa \\ \hline
      \end{tabular}}
\end{table}

>>>>

\author[
    addressref={aff1,aff3},
    %noteref={n1},
    email={jan.freudenthal@uni-wuerzburg.de}
    ]{\inits{JAF}\fnm{Jan A} \snm{Freudenthal}}
\author[
    addressref={aff1,aff2},
    email={simon-pfaff@gmx.de}
    ]{\inits{SP}\fnm{Simon} \snm{Pfaff}}
\author[
   addressref={aff1,aff3},
   email={niklas.terhoeven@uni-wuerzburg.de}
]{\inits{NT}\fnm{Niklas} \snm{Terhoeven}}
\author[
   addressref={aff1},
   email={arthur.korte@uni-wuerzburg.de}
]{\inits{AK}\fnm{Arthur} \snm{Korte}}
\author[
   addressref={aff1,aff3,aff4 },
   noteref={n2},
   email={markus.ankenbrand@uni-wuerzburg.de}
]{\inits{MJA}\fnm{Markus J} \snm{Ankenbrand}}
\author[
   addressref={aff1,aff2,aff5,aff6},                   % id's of addresses, e.g. {aff1,aff2}
   corref={aff6},                       % id of corresponding address, if any
   noteref={n2},                        % id's of article notes, if any
   email={frank.foerster@computational.bio.uni-giessen.de}   % email address
]{\inits{FF}\fnm{Frank} \snm{Förster}}

@@

\address[id=aff3]{%
  \orgname{AnaLife Data Science},
  \street{Wiesengrund 16},
  \postcode{97295 Waldbrunn}
  \city{W\"{u}rzburg},
  \cny{Germany}
}
\address[id=aff2]{%                           % unique id
  \orgname{Department of Bioinformatics, University of W\"{u}rzburg}, % university, etc
  \street{Biozentrum, Am Hubland},                     %
  \postcode{97074},                                % post or zip code
  \city{W\"{u}rzburg},                              % city
  \cny{Germany}                                    % country
}
\address[id=aff4]{%
  \orgname{Chair of Cellular and Molecular Imaging, Comprehensive Heart Failure Center, University Hospital W\"{u}rzburg},
  \street{Josef-Schneider-Str.\ 2},
  \postcode{97080}
  \city{W\"{u}rzburg},
  \cny{Germany}
}
\address[id=aff5]{%
  \orgname{Fraunhofer IME-BR},
  \street{Winchester Str.\ 2},
  \postcode{35394}
  \city{Gie\ss{}en},
  \cny{Germany}
}
\address[id=aff6]{%
  \orgname{Bioinformatics Core Facility of the University of Gie\ss{}en},
  \street{Heinrich-Buff-Ring 58},
  \postcode{35392}
  \city{Gie\ss{}en},
  \cny{Germany}
}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                          %%
%% The Abstract begins here                 %%
%%                                          %%
%% Please refer to the Instructions for     %%
%% authors on http://www.biomedcentral.com  %%
%% and include the section headings         %%
%% accordingly for your article type.       %%
%%                                          %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstractbox}
\begin{abstract} % abstract
%One or two sentences providing a basic introduction to the field, comprehensible to a scientist in any discipline.
Chloroplasts are intracellular organelles that enable plants to conduct photosynthesis. They arose through the symbiotic integration of a prokaryotic cell into an eukaryotic host cell and still contain their own genomes with distinct genomic information.
Plastid genomes accommodate essential genes and are regularly utilized in biotechnology or phylogenetics.
%Two to three sentences of more detailed background, comprehensible to scientists in related disciplines.
Different assemblers that are able to asses the plastid genome, have been developed.
These assemblers often use data of whole genome sequencing experiments, which usually contain reads from the complete chloroplast genome.

%One sentence clearly stating the general problem being addressed by this particular study.
The performance of different assembly tools has never been systematically compared. %to each other concerning success rate or computational requirements.
%One sentence summarising the main result (with the words “here we show” or their equivalent).
Here we present a benchmark of seven chloroplast assembly tools, capable to succeed in more than \SI{60}{\percent} of known real data sets.
%Two or three sentences explaining what the main result reveals in direct comparison to what was thought to be the case previously, or how the main result adds to previous knowledge.
Our results show significant differences between the tested assemblers in terms of generating whole chloroplast genome sequences and computational requirements.
The examination of \num{105} data sets from species with unknown plastid genomes led to the assembly of \num{20} novel chloroplast genomes.
%\todo{on the novel set we only have 49/105 which is roughly 47 percent}
%One or two sentences to put the results into a more general context. 
We created docker images for each tested tool that are freely available for the scientific community and ensure reproducibility of the analyses.
These containers allow to analyze and screen data sets for chloroplast genomes using standard computational infrastructure.
%Two or three sentences to provide a broader perspective, readily comprehensible to a scientist in any discipline, may be included in the first paragraph if the editor considers that the accessibility of the paper is significantly enhanced by their inclusion. 
Thus, large scale screening for chloroplasts as hidden treasures within genomic sequencing data is feasible.

@@

For three assemblies, that were obtained by different assemblers, but not by \go{}, we kept one assembly obtained by \np{} and two from \fp{}.
All resulting \num{49} sequences have been annotated with GeSeq \cite{geseq}. 
The median number of distinct genes annotated were 80 for coding sequences, 4 for rRNA and 27 for tRNA (\cref{tab:feature_count_novel}, \cref{fig:feature_count_novel}). 
All sequences were stored in our repository \zenodorepo{}.
To avoid multi submissions of the same sequence to Genbank, all \num{49} sequences have been inspected against Genbank database via BLAST.
Finally, \num{20} sequences were uploaded to NCBI TPA:inferential (\cref{tab:accessions_suppl}) as novel chloroplast genomes.

@@

We observed no phylogenetic pattern in the success rate of the assemblers (\cref{fig:tree}).
This indicates that the tools are generally able to reconstruct chloroplast genomes across the plant kingdom even without available reference genomes.

@@

\section*{Methods}
\subsection*{Data availability}
Source code for all methods used is available at \cite{github-benchmark-repo} and archived in zenodo under \zenodorepo{}.
All used assembly tools are hosted on GitHub (\cref{tab:toolsversions}) and are encapsulated in docker containers.
That docker containers are published on dockerhub \cite{dockerhub-benchmark} and are named with a leading \texttt{benchmark\_} (\cref{tab:dockerimages_suppl}).

@@

\subsubsection*{Real data}
We selected real data deposited at SRA \cite{sra2010}.
We searched all data that matched \texttt{((((((("green plants"[orgn]) AND "wgs"[Strategy]) AND "illumina"[Platform]) AND "biomol dna"[Properties]) AND "paired"[Layout]) AND "random"[Selection])) AND "public"[Access]}\cite{sra_search_term}. 
For each species with a reference chloroplast in CpBase \cite{cpbase}, we selected one data set.
In total, this amounted to \num{369} data sets (\cref{tab:real_dataset_details}) representing a broad spectrum of the green plants (\cref{fig:tree}).

@@

\subsection*{Evaluation Criteria}
\subsubsection*{Computational Resources}
%Due to computational resources are limited, we evaluated the effect of different input parameters.
We recorded the mean and the peak CPU usage, the peak memory consumption, and the size of the assembly folder for each program. 
As input data, we used different data sets comprising \numlist{25000;250000;2500000} read pairs sampled from  our simulated reads.
%Therefore, the simulated perfect read files have been read repeatedly to achieve the required number of read pairs.
We used our docker image setup (\cref{tab:dockerimages_suppl}) to run all assembly programs three times for each parameter setting.
The different settings combined different input data and different number of threads to use (\numlist{1;2;4;8}).

@@

\begin{table}[h!]
\caption{\textbf{Tools and version information used in our benchmark setup} All tools are wrapped into docker containers and stored on dockerhub \cite{dockerhub-benchmark}. The corresponding tags and SHA256 checksums are reported in \cref{tab:dockerimages_suppl}}
\label{tab:toolsversions}
\centering
      \resizebox{\textwidth}{!}{\begin{tabular}{llc}
        \hline
        Tool & Source Repository & Commit used for benchmarking \\ \hline
        \go & \url{https://github.com/Kinggerm/GetOrganelle.git} & \texttt{587c1c51c34e270eb9178a42a77a5150157e6925} \\
        \ioga & \url{https://github.com/holmrenser/IOGA.git} & \texttt{c460ea9d9fe176fec2bd76d369b0cbb36793b2bf} \\
        \np & \url{https://github.com/ndierckx/NOVOPlasty.git} & \texttt{6af0894f8ea1d76a1b71df9cb762cf6e48dceac1} \\
        \ce & \url{https://github.com/chloroExtractorTeam/chloroExtractor.git} & \texttt{87364e48ec84a3f6ee91fc8d995b0bda5a0fa82d} \\
        \cassp & \url{https://github.com/eead-csic-compbio/chloroplast_assembly_protocol.git} & \texttt{250d16ac02005d6a5939bf182b3d2995d0e88229} \\
        \fp & \url{https://github.com/mrmckain/Fast-Plast.git} & \texttt{7e32b2e797fd1f49d32d6559e8345afefbaff803} \\
        \oa & \url{https://git.metabarcoding.org/org-asm/org-asm.git} & \texttt{830313acae3ca773b63f6bea9fc6d017e021bde5} \\ \hline
%          Tool & Image name and tag\\ \hline
%          \ce & \dockerce \\
%          \cassp & \dockercassp \\
%          \fp & \dockerfp \\
%          \go & \dockergo \\
%          \ioga & \dockerioga \\
%          \np & \dockernp \\
%          \oa & \dockeroa \\ \hline
      \end{tabular}}
\end{table}
